We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-07 paper/paper.tex
galaxias

We use three dimentional positions as reported by. 
The appendix includes the tables with the values we use in our
computations.
For each central galaxy we use the 15 brightest satellites within a
distance of $300$kpc to the central galaxy.
The satellites for the MW are: 
THe satellites for M31 are:

>>>>

The base for our analysis is the catalog compiled in
\citep{2014yCat..74351928P} which reports information on all 
galaxies within 3 Mpc around the Sun to that date. 
Detailed description of the compiled catalog can be found in
\citep{2013MNRAS.435.1928P}, here we summarize the relevant features
for the current study.

The information in the catalog is based on the catalogue compiled by
\cite{2012AJ....144....4M}.
The distance estimate are based on resolved stellar populations. 
We use three dimensional positions in a cartesian Coordinate system
as computed by \cite{2013MNRAS.435.1928P}.
In this coordinate system the $z$-axis points toward the Galactic north pole, the
$x-$-axis points in the direction from the Sun to the Galactic centre,
and the $y$-axis points in the direction of the Galactic rotation.

For both the M31 and MW we only use the 11 to 15 brightest satellites(using
$M_V$ magnitudes) within a distance of $300$kpc to its central galaxy.
The satellites included for the MW analysis are: 
LMC, SMC, Canis Major, Sagittarius dSph, Fornax, Leo I, Sculptor,
Leo II, Sextans I, Carina, Ursa Minor, Draco, Canes Venatici (I),
Hercules and Bootes II.
The satellites included for the MW analysis are: Triangulum, NGC205,
M32, IC10, NGC185, NGC147, Andromeda VII, Andromeda II, Andromeda
XXXII, Andromeda XXXI, Andromeda I, Andromeda VI, Andromeda XXIII, LGS 3, 
 and Andromeda III.
